---
title: "Shark Tank"
author: "Michael Cao"
date: "2023-04-04"
output:
  html_document: default
  word_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Summary of NA entries in each column (original data)
```{r}
dat <- read.csv("Shark Tank US dataset.csv")
dat.copy <- dat
dim(dat)
colSums(is.na(dat))
```



Inspect each column
```{r}
table(dat$Season.Number) #good
table(dat$Episode.Number) #good
table(dat$Season.Start) #good
which(dat$Startup.Name=='') #good
table(dat$Industry) #good
sum(dat$Business.Description=='') #good
sum(dat$Entrepreneur.Names=='') # missing names - but okay
table(dat$Original.Ask.Amount) #good
table(dat$Original.Offered.Equity) #good
table(dat$Valuation.Requested) #good
table(dat$Got.Deal) #good


table(dat$Season.End) #need to fix
sum(dat$Original.Air.Date == '') #need to fix
table(dat$Pitchers.Gender) #need to fix
sum(dat$Pitchers.City=='') #599 missing cities - hard to fix
sum(dat$Pitchers.State=='') #358 missing states - hard to fix
table(dat$Pitchers.Average.Age) #984 missing ages - to be removed
table(dat$Company.Website=='') #inaccurate column - to be removed
sum(is.na(dat$Multiple.Entrepreneurs)) #need to convert the 478 NAs
sum(is.na(dat$US.Viewership)) #useless column - to be removed


# take special note of the following columns (loan/royalty deals)
range(dat$Total.Deal.Amount, na.rm=T) #convert NA to 0 or not??
which(dat$Total.Deal.Amount==0) #need to fix row 641
range(dat$Total.Deal.Equity, na.rm=T)
which(dat$Total.Deal.Equity==0) 
range(dat$Deal.Valuation, na.rm=T)
which(dat$Deal.Valuation==0)
range(dat$Investment.Amount.Per.Shark, na.rm=T)
which(dat$Investment.Amount.Per.Shark==0) #row 641 again
table(dat$Royalty.Deal) #convert all NAs to 0
table(dat$Loan) #need to fix


#lastly, we need to fix/ fill NAs for the individual shark columns
sum(is.na(dat$Barbara.Corcoran.Present))
table(dat$Barbara.Corcoran.Present)
table(dat$Barbara.Corcoran.Investment.Amount)
table(dat$Barbara.Corcoran.Investment.Equity)
```



Remove Pitchers.Average.Age, Company.Website, US.Viewership columns
```{r}
dim(dat)
dat <- dat[, !names(dat) %in% 
             c("Pitchers.Average.Age", "Company.Website", "US.Viewership")]
dim(dat)
```



Fill in missing season dates and reformatting
```{r}
table(dat$Season.Start)
dat$Season.Start <- format(as.Date(dat$Season.Start, format = '%d-%b-%y'), '%m/%d/%Y')
table(dat$Season.Start)

table(dat$Season.End)
which(dat$Season.End=='')
dat$Season.End[which(dat$Season.End=='')] <- '20-Apr-23'
dat$Season.End <- format(as.Date(dat$Season.End, format = '%d-%b-%y'), '%m/%d/%Y')
table(dat$Season.End)
```



Fix the episode air date column (Manually)
```{r}
sum(dat$Original.Air.Date == '')

rows_with_na <- which(dat$Original.Air.Date=='')
eps_with_na <- unique(dat[rows_with_na, c('Season.Number', 'Episode.Number')])
eps_with_na

dat[dat$Season.Number==9 & dat$Episode.Number==17, 'Original.Air.Date'] <- '14-Jan-18'
dat[dat$Season.Number==9 & dat$Episode.Number==18, 'Original.Air.Date'] <- '21-Jan-18'
dat[dat$Season.Number==9 & dat$Episode.Number==19, 'Original.Air.Date'] <- '28-Jan-18'
dat[dat$Season.Number==9 & dat$Episode.Number==20, 'Original.Air.Date'] <- '28-Jan-18'
dat[dat$Season.Number==9 & dat$Episode.Number==21, 'Original.Air.Date'] <- '11-Feb-18'
dat[dat$Season.Number==9 & dat$Episode.Number==22, 'Original.Air.Date'] <- '18-Feb-18'
dat[dat$Season.Number==9 & dat$Episode.Number==23, 'Original.Air.Date'] <- '25-Feb-18'

dat[dat$Season.Number==10 & dat$Episode.Number==2, 'Original.Air.Date'] <- '14-Oct-18'
dat[dat$Season.Number==10 & dat$Episode.Number==3, 'Original.Air.Date'] <- '21-Oct-18'
dat[dat$Season.Number==10 & dat$Episode.Number==4, 'Original.Air.Date'] <- '28-Oct-18'
dat[dat$Season.Number==10 & dat$Episode.Number==5, 'Original.Air.Date'] <- '18-Nov-18'
dat[dat$Season.Number==10 & dat$Episode.Number==6, 'Original.Air.Date'] <- '25-Nov-18'
dat[dat$Season.Number==10 & dat$Episode.Number==7, 'Original.Air.Date'] <- '02-Dec-18'
dat[dat$Season.Number==10 & dat$Episode.Number==9, 'Original.Air.Date'] <- '06-Jan-19'
dat[dat$Season.Number==10 & dat$Episode.Number==12, 'Original.Air.Date'] <- '27-Jan-19'
dat[dat$Season.Number==10 & dat$Episode.Number==13, 'Original.Air.Date'] <- '27-Jan-19'
dat[dat$Season.Number==10 & dat$Episode.Number==14, 'Original.Air.Date'] <- '03-Mar-19'
dat[dat$Season.Number==10 & dat$Episode.Number==15, 'Original.Air.Date'] <- '10-Mar-19'
dat[dat$Season.Number==10 & dat$Episode.Number==16, 'Original.Air.Date'] <- '17-Mar-19'
dat[dat$Season.Number==10 & dat$Episode.Number==17, 'Original.Air.Date'] <- '24-Mar-19'
dat[dat$Season.Number==10 & dat$Episode.Number==18, 'Original.Air.Date'] <- '07-Apr-19'
dat[dat$Season.Number==10 & dat$Episode.Number==19, 'Original.Air.Date'] <- '14-Apr-19'
dat[dat$Season.Number==10 & dat$Episode.Number==20, 'Original.Air.Date'] <- '21-Apr-19'
dat[dat$Season.Number==10 & dat$Episode.Number==21, 'Original.Air.Date'] <- '28-Apr-19'
dat[dat$Season.Number==10 & dat$Episode.Number==22, 'Original.Air.Date'] <- '05-May-19'

dat[dat$Season.Number==11 & dat$Episode.Number==2, 'Original.Air.Date'] <- '06-Oct-19'
dat[dat$Season.Number==11 & dat$Episode.Number==4, 'Original.Air.Date'] <- '20-Oct-19'
dat[dat$Season.Number==11 & dat$Episode.Number==5, 'Original.Air.Date'] <- '27-Oct-19'
dat[dat$Season.Number==11 & dat$Episode.Number==6, 'Original.Air.Date'] <- '03-Nov-19'
dat[dat$Season.Number==11 & dat$Episode.Number==7, 'Original.Air.Date'] <- '10-Nov-19'
dat[dat$Season.Number==11 & dat$Episode.Number==8, 'Original.Air.Date'] <- '17-Nov-19'
dat[dat$Season.Number==11 & dat$Episode.Number==9, 'Original.Air.Date'] <- '01-Dec-19'
dat[dat$Season.Number==11 & dat$Episode.Number==10, 'Original.Air.Date'] <- '05-Jan-20'
dat[dat$Season.Number==11 & dat$Episode.Number==11, 'Original.Air.Date'] <- '12-Jan-20'
dat[dat$Season.Number==11 & dat$Episode.Number==12, 'Original.Air.Date'] <- '19-Jan-20'
dat[dat$Season.Number==11 & dat$Episode.Number==13, 'Original.Air.Date'] <- '28-Feb-20'
dat[dat$Season.Number==11 & dat$Episode.Number==14, 'Original.Air.Date'] <- '06-Mar-20'
dat[dat$Season.Number==11 & dat$Episode.Number==15, 'Original.Air.Date'] <- '13-Mar-20'
dat[dat$Season.Number==11 & dat$Episode.Number==16, 'Original.Air.Date'] <- '20-Mar-20'
dat[dat$Season.Number==11 & dat$Episode.Number==17, 'Original.Air.Date'] <- '27-Mar-20'
dat[dat$Season.Number==11 & dat$Episode.Number==18, 'Original.Air.Date'] <- '03-Apr-20'
dat[dat$Season.Number==11 & dat$Episode.Number==19, 'Original.Air.Date'] <- '10-Apr-20'
dat[dat$Season.Number==11 & dat$Episode.Number==21, 'Original.Air.Date'] <- '06-May-20'
dat[dat$Season.Number==11 & dat$Episode.Number==22, 'Original.Air.Date'] <- '08-May-20'
dat[dat$Season.Number==11 & dat$Episode.Number==23, 'Original.Air.Date'] <- '13-May-20'

dat[dat$Season.Number==14 & dat$Episode.Number==4, 'Original.Air.Date'] <- '14-Oct-22'
dat[dat$Season.Number==14 & dat$Episode.Number==5, 'Original.Air.Date'] <- '21-Oct-22'
dat[dat$Season.Number==14 & dat$Episode.Number==6, 'Original.Air.Date'] <- '11-Nov-22'
dat[dat$Season.Number==14 & dat$Episode.Number==7, 'Original.Air.Date'] <- '18-Nov-22'

dat$Original.Air.Date <- format(as.Date(dat$Original.Air.Date, 
                                        format = '%d-%b-%y'), '%m/%d/%Y')
sum(dat$Original.Air.Date == '')
```



Fix the Gender column
```{r}
table(dat$Pitchers.Gender)
rows <- which(dat$Pitchers.Gender=='')
dat[rows, 'Entrepreneur.Names']
dat$Pitchers.Gender[rows] <- c('Male', 'Male', 'Male', 'Mixed Team', 'Male', 'Male')
dat$Pitchers.Gender[dat$Pitchers.Gender=='Mixed Team'] <- 'Mixed'
table(dat$Pitchers.Gender)
```



Re-numbering Pitch.Number
```{r}
range(dat$Pitch.Number)
tail(dat$Pitch.Number)
which(!(1:1097 %in% dat$Pitch.Number))
dat$Pitch.Number <- 1:1097
```



Convert NAs in Multiple.Entrepreneurs
```{r}
sum(is.na(dat$Multiple.Entrepreneurs))
table(dat$Multiple.Entrepreneurs)
dat$Multiple.Entrepreneurs[is.na(dat$Multiple.Entrepreneurs)] <- 0
table(dat$Multiple.Entrepreneurs)
```



Convert NAs in Number.of.sharks.in.deal
```{r}
sum(is.na(dat$Number.of.sharks.in.deal))
table(dat$Number.of.sharks.in.deal)
dat$Number.of.sharks.in.deal[is.na(dat$Number.of.sharks.in.deal)] <- 0
table(dat$Number.of.sharks.in.deal)
```



Fix the Deal columns (to be discussed? should we convert NAs?)
*Row 641: got $50000 loan deal with no amount/equity involved. Should we remove it?*
*Others: loan/royalty-only deal with no equity involved. How to handle?*
```{r}
table(dat$Total.Deal.Amount)
which(dat$Total.Deal.Amount==0) # got a deal, but total amount is 0
dat$Total.Deal.Amount[is.na(dat$Total.Deal.Amount)] <- 0
table(dat$Total.Deal.Amount)

table(dat$Total.Deal.Equity)
which(dat$Total.Deal.Equity==0) # got a deal, but total equity is 0
dat$Total.Deal.Equity[is.na(dat$Total.Deal.Equity)] <- 0
table(dat$Total.Deal.Equity)

table(dat$Deal.Valuation)
which(dat$Deal.Valuation==0) # got a deal, but deal valuation is 0
dat$Deal.Valuation[is.na(dat$Deal.Valuation)] <- 0
table(dat$Deal.Valuation)

table(dat$Investment.Amount.Per.Shark)
which(dat$Investment.Amount.Per.Shark==0) #row 641 again
dat$Investment.Amount.Per.Shark[is.na(dat$Investment.Amount.Per.Shark)] <- 0
table(dat$Investment.Amount.Per.Shark)

table(dat$Equity.Per.Shark)
which(dat$Equity.Per.Shark==0) #same situation
dat$Equity.Per.Shark[is.na(dat$Equity.Per.Shark)] <- 0
table(dat$Equity.Per.Shark)
```



Convert NAs in Royalty.Deal 
```{r}
sum(is.na(dat$Royalty.Deal))
table(dat$Royalty.Deal)
dat$Royalty.Deal[is.na(dat$Royalty.Deal)] <- 0
table(dat$Royalty.Deal)
```



Fix the Loan column (to be discussed?)
*Some orginially has the amount, most do not*
```{r}
sum(is.na(dat$Loan))
table(dat$Loan)
dat$Loan[is.na(dat$Loan)] <- 0
dat$Loan[dat$Loan!=0] <- 1
table(dat$Loan)
```



Update missing Shark Attendance (Manually) 
*It is worth noting that this dataset is missing many episodes*
```{r}
cols <- grep("Present$", colnames(dat))
rows_with_na <- which(apply(dat[,cols], 1, function(x) any(is.na(x))))
eps_with_na <- unique(dat[rows_with_na, c('Season.Number', 'Episode.Number')])
eps_with_na 

# [1] "Barbara.Corcoran.Present"
# [2] "Mark.Cuban.Present"      
# [3] "Lori.Greiner.Present"    
# [4] "Robert.Herjavec.Present" 
# [5] "Daymond.John.Present"    
# [6] "Kevin.O.Leary.Present"  

dat[dat$Season.Number==11 & 
      dat$Episode.Number==1, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==2, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==3, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==4, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==5, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==6, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==7, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==8, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==9, cols] <- matrix(c(1,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==10, cols] <- matrix(c(1,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==11, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==12, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==13, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==14, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==15, cols] <- matrix(c(1,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==16, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==17, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==18, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==19, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==20, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==21, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==22, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==23, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==11 & 
      dat$Episode.Number==24, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==1, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==2, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==3, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==4, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==5, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==6, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==7, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==8, cols] <- matrix(c(1,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==9, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==12 & 
      dat$Episode.Number==10, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==1, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==2, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==3, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==4, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==5, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==6, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==7, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==8, cols] <- matrix(c(1,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==9, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==13 & 
      dat$Episode.Number==10, cols] <- matrix(c(1,1,1,0,0,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==1, cols] <- matrix(c(1,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==2, cols] <- matrix(c(1,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==3, cols] <- matrix(c(0,1,1,0,1,1),3,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==4, cols] <- matrix(c(0,1,1,1,1,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==5, cols] <- matrix(c(0,1,1,1,0,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==6, cols] <- matrix(c(0,1,1,0,1,1),4,6,byrow=T)
dat[dat$Season.Number==14 & 
      dat$Episode.Number==7, cols] <- matrix(c(1,1,1,1,0,1),3,6,byrow=T)

sum(is.na(dat[,cols]))
table(dat$Barbara.Corcoran.Present)
table(dat$Mark.Cuban.Present)
table(dat$Lori.Greiner.Present)
table(dat$Robert.Herjavec.Present)
table(dat$Daymond.John.Present)
table(dat$Kevin.O.Leary.Present)
```



Convert NAs in Investment Amount/Equity columns to 0
```{r}
cols <- grep("(Investment.Amount|Investment.Equity)$", colnames(dat))
colSums(is.na(dat[, cols])) 

for (i in cols)
{
  dat[is.na(dat[, i]), i] <- 0
}

colSums(is.na(dat[, cols]))
```



If we want to fill in city/state info, we can do it manually...
```{r}
sum(dat$Pitchers.City=='') #599 missing cities - need to fix manually
sum(dat$Pitchers.State=='') #358 missing states - need to fix manually
```

No NAs in the processed data
```{r}
colSums(is.na(dat))
```



Convert the processed dataframe to csv format
```{r}
if (!dir.exists("data")) 
{
  dir.create("data")
}

# raw data
write.csv(dat.copy, "data/Shark Tank Original.csv", row.names = FALSE)

# processed data
write.csv(dat, "data/Shark Tank Processed.csv", row.names = FALSE)

# separated by shark presence
kevin <- dat[dat$Kevin.O.Leary.Present==1,]
barbara <- dat[dat$Barbara.Corcoran.Present==1,]
mark <- dat[dat$Mark.Cuban.Present==1,]
daymond <- dat[dat$Daymond.John.Present==1,]
lori <- dat[dat$Lori.Greiner.Present==1,]
robert <- dat[dat$Robert.Herjavec.Present==1,]

write.csv(kevin, "data/Kevin.csv", row.names = FALSE)
write.csv(barbara, "data/Barbara.csv", row.names = FALSE)
write.csv(mark, "data/Mark.csv", row.names = FALSE)
write.csv(daymond, "data/Daymond.csv", row.names = FALSE)
write.csv(lori, "data/Lori.csv", row.names = FALSE)
write.csv(robert, "data/Robert.csv", row.names = FALSE)
```



Visualization 1: Median investment amount by shark
```{r}
colors <- c("#4C97DB", "#2CC6A0", "#F4D03F", "#B67BDC", "#F7931E", "#FF616D")
plot(aggregate(kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Kevin.O.Leary.Investment.Amount ~ kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Season.Number, kevin[kevin$Kevin.O.Leary.Investment.Amount>0,], median), type='o', pch=19, lwd=2, ylim=c(0, 300000), cex.lab=0.8, axes=F, col = colors[1], xlab='', ylab='')
lines(aggregate(barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Barbara.Corcoran.Investment.Amount ~ barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Season.Number, barbara[barbara$Barbara.Corcoran.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col = colors[2])
lines(aggregate(robert[robert$Robert.Herjavec.Investment.Amount>0,]$Robert.Herjavec.Investment.Amount ~ robert[robert$Robert.Herjavec.Investment.Amount>0,]$Season.Number, robert[robert$Robert.Herjavec.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col = colors[3])
lines(aggregate(lori[lori$Lori.Greiner.Investment.Amount>0,]$Lori.Greiner.Investment.Amount ~ lori[lori$Lori.Greiner.Investment.Amount>0,]$Season.Number, lori[lori$Lori.Greiner.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col = colors[4])
lines(aggregate(daymond[daymond$Daymond.John.Investment.Amount>0,]$Daymond.John.Investment.Amount ~ daymond[daymond$Daymond.John.Investment.Amount>0,]$Season.Number, daymond[daymond$Daymond.John.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col = colors[5])
lines(aggregate(mark[mark$Mark.Cuban.Investment.Amount>0,]$Mark.Cuban.Investment.Amount ~ mark[mark$Mark.Cuban.Investment.Amount>0,]$Season.Number, mark[mark$Mark.Cuban.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col = colors[6])
axis(side = 1, at = 1:14, cex.axis = 0.6, tcl= -0.2, mgp= c(0,0.2,0))
axis(side = 2, at = seq(0, 300000, 25000), cex.axis = 0.6, mgp= c(0,0.5,0), las=2, tcl= -0.2)
mtext('Median Investment Amount ($)', side = 2, line=2.5, cex=0.7, font=14)
mtext("Season", side = 1, line = 1.2, cex=0.7, font=14)
legend("topleft", legend = c('Kevin', 'Barbara', 'Robert', 'Lori', 'Daymond', 'Mark'), col = colors, lty = 1, lwd = 2, cex=.5, inset = c(0.02, 0))
```


Visualization 2: Median investment equity by shark
```{r}
colors <- c("#4C97DB", "#2CC6A0", "#F4D03F", "#B67BDC", "#F7931E", "#FF616D")
plot(aggregate(kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Kevin.O.Leary.Investment.Equity ~ kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Season.Number, kevin[kevin$Kevin.O.Leary.Investment.Amount>0,], median), type='o', pch=19, lwd=2, xlab='', ylab='', ylim=c(0, 40), cex.lab=0.8, axes=F, col= colors[1])
lines(aggregate(barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Barbara.Corcoran.Investment.Equity ~ barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Season.Number, barbara[barbara$Barbara.Corcoran.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col=colors[2])
lines(aggregate(robert[robert$Robert.Herjavec.Investment.Amount>0,]$Robert.Herjavec.Investment.Equity ~ robert[robert$Robert.Herjavec.Investment.Amount>0,]$Season.Number, robert[robert$Robert.Herjavec.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col=colors[3])
lines(aggregate(lori[lori$Lori.Greiner.Investment.Amount>0,]$Lori.Greiner.Investment.Equity ~ lori[lori$Lori.Greiner.Investment.Amount>0,]$Season.Number, lori[lori$Lori.Greiner.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col=colors[4])
lines(aggregate(daymond[daymond$Daymond.John.Investment.Amount>0,]$Daymond.John.Investment.Equity ~ daymond[daymond$Daymond.John.Investment.Amount>0,]$Season.Number, daymond[daymond$Daymond.John.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col=colors[5])
lines(aggregate(mark[mark$Mark.Cuban.Investment.Amount>0,]$Mark.Cuban.Investment.Equity ~ mark[mark$Mark.Cuban.Investment.Amount>0,]$Season.Number, mark[mark$Mark.Cuban.Investment.Amount>0,], median), type='o', pch=19, lwd=2, col=colors[6])

axis(side = 1, at = 1:14, cex.axis = 0.6, tcl= -0.2, mgp= c(0,0.2,0))
axis(side = 2, at = seq(0, 40, 5), cex.axis = 0.6, las=2, tcl= -0.2, mgp= c(0,0.5,0))
mtext('Median Investment Equity (%)', side = 2, line=1.5, cex=0.7, font=14)
mtext("Season", side = 1, line = 1.2, cex=0.7, font=14)
legend("topright", legend = c('Kevin', 'Barbara', 'Robert', 'Lori', 'Daymond', 'Mark'), col = colors, lty = 1, lwd = 2, cex=.5, inset = c(0.03, 0))
```



Visualization 3: Shark's Willingness to make a deal
```{r}
colors <- c("#4C97DB", "#2CC6A0", "#F4D03F", "#B67BDC", "#F7931E", "#FF616D")
pitch_per_season <- tapply(dat$Season.Number, dat$Season.Number, FUN = length)/100

plot(tapply(kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Kevin.O.Leary.Investment.Amount, kevin[kevin$Kevin.O.Leary.Investment.Amount>0,]$Season.Number, FUN = length)/pitch_per_season, type='o', pch=19, lwd=2, xlab='', ylab='', ylim=c(0, 30), cex.lab=0.8, axes=F, col=colors[1])
lines(tapply(barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Barbara.Corcoran.Investment.Amount, barbara[barbara$Barbara.Corcoran.Investment.Amount>0,]$Season.Number, FUN = length)/pitch_per_season, type='o', pch=19, lwd=2, col=colors[2])
lines(tapply(robert[robert$Robert.Herjavec.Investment.Amount>0,]$Robert.Herjavec.Investment.Amount, robert[robert$Robert.Herjavec.Investment.Amount>0,]$Season.Number, FUN = length)/pitch_per_season, type='o', pch=19, lwd=2, col=colors[3])
lines(c(NA, NA, tapply(lori[lori$Lori.Greiner.Investment.Amount>0,]$Lori.Greiner.Investment.Amount, lori[lori$Lori.Greiner.Investment.Amount>0,]$Season.Number, FUN = length))/pitch_per_season, type='o', pch=19, lwd=2, col=colors[4])
lines(tapply(daymond[daymond$Daymond.John.Investment.Amount>0,]$Daymond.John.Investment.Amount, daymond[daymond$Daymond.John.Investment.Amount>0,]$Season.Number, FUN = length)/pitch_per_season, type='o', pch=19, lwd=2, col=colors[5])
lines(c(NA,tapply(mark[mark$Mark.Cuban.Investment.Amount>0,]$Mark.Cuban.Investment.Amount, mark[mark$Mark.Cuban.Investment.Amount>0,]$Season.Number, FUN = length))/pitch_per_season, type='o', pch=19, lwd=2, col=colors[6])
axis(side = 1, at = 1:14, cex.axis = 0.6, tcl= -0.2, mgp= c(0,0.2,0))
axis(side = 2, at = seq(0, 30, 2), cex.axis = 0.6, las=2, tcl= -0.2, mgp= c(0,0.5,0))
mtext('Deal per Pitch (%)', side = 2, line=1.5, cex=0.7, font=14)
mtext("Season", side = 1, line = 1.2, cex=0.7, font=14)
legend("topleft", legend = c('Kevin', 'Barbara', 'Robert', 'Lori', 'Daymond', 'Mark'), col = colors, lty = 1, lwd = 2, cex=.5, inset = c(0.02, 0))
```



Visualization 4: barplot of median investment, equity, and deal per pitch by shark
```{r}
par(mar=c(5, 4, 4, 5)+.1)

colors <- c("#FFA600", "#7FDBFF", "#2ECC40", "#F012BE", "#FFDC00", "#FF4136")

median_investment <- c(median(kevin$Kevin.O.Leary.Investment.Amount[kevin$Kevin.O.Leary.Investment.Amount>0]), median(barbara$Barbara.Corcoran.Investment.Amount[barbara$Barbara.Corcoran.Investment.Amount>0]), median(robert$Robert.Herjavec.Investment.Amount[robert$Robert.Herjavec.Investment.Amount>0]), median(lori$Lori.Greiner.Investment.Amount[lori$Lori.Greiner.Investment.Amount>0]), median(daymond$Daymond.John.Investment.Amount[daymond$Daymond.John.Investment.Amount>0]),median(mark$Mark.Cuban.Investment.Amount[mark$Mark.Cuban.Investment.Amount>0]))

median_equity <- c(median(kevin$Kevin.O.Leary.Investment.Equity[kevin$Kevin.O.Leary.Investment.Equity>0]), median(barbara$Barbara.Corcoran.Investment.Equity[barbara$Barbara.Corcoran.Investment.Equity>0]), median(robert$Robert.Herjavec.Investment.Equity[robert$Robert.Herjavec.Investment.Equity>0]), median(lori$Lori.Greiner.Investment.Equity[lori$Lori.Greiner.Investment.Equity>0]), median(daymond$Daymond.John.Investment.Equity[daymond$Daymond.John.Investment.Equity>0]),median(mark$Mark.Cuban.Investment.Equity[mark$Mark.Cuban.Investment.Equity>0]))

deal_percent <- c(mean(kevin$Kevin.O.Leary.Investment.Amount>0),
                  mean(barbara$Barbara.Corcoran.Investment.Amount>0),
                  mean(robert$Robert.Herjavec.Investment.Amount>0),
                  mean(lori$Lori.Greiner.Investment.Amount>0),
                  mean(daymond$Daymond.John.Investment.Amount>0),
                  mean(mark$Mark.Cuban.Investment.Amount>0))

bp <- barplot(
  height = cbind(median_investment/10000, median_equity*1, deal_percent*100),
  beside = TRUE, ylim = c(0,27), cex.names=.7, font=14,
  col = colors, axes = F)

axis(side = 2, at = seq(0, 27, 5), cex.axis = 0.6, las=2, tcl= -0.2, mgp= c(0,0.5,0))
axis(side = 4, at = seq(0, 27, 2.5), cex.axis = 0.6, las=2, tcl= -0.2, mgp= c(0,0.5,0))
abline(h=0)
mtext('Amount (10^4 USD)', side = 2, line=1.2, cex=0.6, font=14)
mtext('Percentage (%)', side = 4, line=1.5, cex=0.6, font=14)
mtext(text = c("Median Investment (10^4 USD)", "Median Equity (%)", "Deal per Pitch (%)"), side = 1, line = 0.2, at = c(4, 11, 18), cex = 0.7, font=14)

text(x = bp, y = cbind(median_investment/10000, median_equity, deal_percent*100)-.5, labels = round(cbind(median_investment/10000, median_equity, deal_percent*100),2), pos = 3, cex = .4, col = "black")

legend("topleft", legend = c('Kevin', 'Barbara', 'Robert', 'Lori', 'Daymond', 'Mark'), fill = colors, cex=.5, inset = c(0.02, 0.03))

# par.default()
```
